Notes on the low density parameters in {\tt MAESTRO}

### 2011-03-22 docs/lo_density/lo_density.tex
some updates

These are working notes for the low density parameters in {\tt MAESTRO}.

@@

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}, 
{\tt base\_cutoff\_density\_coord}, and {\tt burning\_cutoff\_density\_coord} by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
or equal to that particular cutoff value (see Figure \ref{Fig:Cutoff}.
We compute the cutoff coordinate at the
coarsest level, and then set the coordinate at the next finer level to be twice that
of the coarser level.  We set the coordinates at the following points in the code:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[hpb]
\centering
\includegraphics[width=4.0in]{\lodensfigpath/cutoff}\hspace{0.2in}
\begin{minipage}[b]{5.0in}
\caption[Relation between cutoff density and cutoff coordinates]
{Image of how the cutoff density and cutoff coordinates
are related.  This is drawn assuming {\tt drdxfac}=5.\vspace{2em}}
\end{minipage}
\label{Fig:Cutoff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\item At the beginning of {\tt advance\_timestep}.

\item After each call to {\tt advect\_base\_dens}.

\item After we ``{\tt correct base}'' (by setting $\rho_0 = \overline{\rho}$ in
  plane-parallel and $\rho_0 = \rho_0 + {\bf{Avg}}(\rho - \rho_0)$ in spherical).

\item At the beginning of the second-half of the algorithm (Step 6), we reset
  the coordinates to the base-time values using $\rho_0^n$.

@@

\item In {\tt sponge}, {\tt anelastic\_cutoff} is used in a problem
  dependent way.

>>>>

These are working notes for the low density parameters in {\tt MAESTRO}.  In low density
regions, we modify the behavior of the algorithm.  Here is a summary of some parameters,
and a brief description of what they do.
\begin{itemize}
\item {\tt base\_cutoff\_density}, $\rho_{\rm base}$, (real):\\ \\
Essentially controls the lowest density allowed in the simulation and modifies the behavior
of several modules.
\item {\tt base\_cutoff\_density\_coord(:)} (integer array):\\ \\
For each level in the radial base state array, this is the coordinate of the first cell
where $\rho_0 < \rho_{\rm base}$.  Slightly more complicated for multilevel problems.
\item {\tt anelastic\_cutoff}, $\rho_{\rm anelastic}$, (real):\\ \\
If $\rho_0 < \rho_{\rm anelastic}$, we modify the computation of $\beta_0$ in the
divergence constraint.
\item {\tt anelastic\_cutoff\_coord(:)} (integer array):\\ \\
Anelastic cutoff analogy of {\tt base\_cutoff\_density\_coord(:)}.
\item {\tt burning\_cutoff\_density}, $\rho_{\rm burning}$,  (real):\\ \\
If $\rho < \rho_{\rm burning}$, don't call the burner in this cell.
\item {\tt burning\_cutoff\_density\_coord(:)} (integer array):\\ \\
Burning cutoff analogy of {\tt base\_cutoff\_density\_coord(:)}.
\item {\tt buoyancy\_cutoff\_factor} (real):\\ \\
When computing velocity forcing, set the buoyance term ($\rho-\rho_0$) to 0 if 
$\rho < $ {\tt buoyancy\_cutoff\_factor} * {\tt base\_cutoff\_density}.
\item {\tt do\_eos\_h\_above\_cutoff} (logical):\\ \\
If {\rm true}, at the end of the advection step, for each cell where 
$\rho < \rho_{\rm base}$, recompute $h = h(\rho,p_0,X)$.
\end{itemize}

@@

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}(:), 
{\tt base\_cutoff\_density\_coord}(:), and {\tt burning\_cutoff\_density\_coord}(:) by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
or equal to that particular cutoff value (see Figure \ref{Fig:Cutoff} for the
single-level case).  Multilevel is more complicated.

We set the coordinates at the following points in the code:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[hpb]
\centering
\includegraphics[width=4.0in]{\lodensfigpath/cutoff}\hspace{0.2in}
\begin{minipage}[b]{5.0in}
\caption[Relation between cutoff density and cutoff coordinates]
{Image of how the cutoff density and cutoff coordinates
are related.  This is drawn assuming {\tt drdxfac}=5.\vspace{2em}}
\end{minipage}
\label{Fig:Cutoff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\item After reading the base state from a checkpoint file when restarting.

\item After regridding.

\item After advancing $\rho_0$ with {\tt advect\_base\_dens}.

\item After advancing $\rho$ and setting $\rho_0 = \overline{\rho}$.

\item At the beginning of the second-half of the algorithm ({\bf Step 6}), we reset
  the coordinates to the base-time values using $\rho_0^n$.

@@

\item Some versions of {\tt sponge}, use {\tt anelastic\_cutoff} in a problem dependent way.
